---
title: "Hexwall"
prefer-html: true
---
# Projects - Hexwall

## Hex file resources

### Shiny App for creating hex
<https://connect.thinkr.fr/hexmake/>

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
#library(data.table)
library(DT)
```

# FIX - get all of these downloaded  
https://github.com/rstudio/hex-stickers  


## load hexwall.R function
```{r hexwall}
source("~/Documents/r-studio-and-git/my_book_again/hexwall.R")

test <- hexwall("~/Documents/r-studio-and-git/my_book_again/my_stickers", sticker_row_size = 7, sticker_width = 200)
test
```



source("~/Documents/r-studio-and-git/my_hex_stickers/hexwall/hexwall.R")
# call hexwall function and assign to "test"
# this sometimes get an error -- try adjusting sticker_row_size
test <- hexwall("~/Documents/r-studio-and-git/my_hex_stickers/my_stickers", sticker_row_size = 7, sticker_width = 200)
test


png("~/Documents/r-studio-and-git/my_hex_stickers/hexwall/samplehex/test123.png")
hexwall("~/Documents/r-studio-and-git/my_hex_stickers/hexwall/samplehex", sticker_row_size = 4, sticker_width = 200)
image_write(test, "~/Documents/r-studio-and-git/my_hex_stickers/hexwall/samplehex/test123.png")
dev.off()


hex_table <- data.table


# FIX - data.table is not working properly -- needs to be fixed
It seems to be reading, but not displaying in data.table format correctly.  
It works within R, but not in Quarto when rendered.  

# FIX - data.table giving a warning about reading in last line  

```{r}
#library(data.table)
hex_table <- datatable(read.csv("~/Documents/r-studio-and-git/my_book_again/my_stickers_data_list/hex_data.csv"))
hex_table

#hex_table_as_tibble <- as_tibble(hex_table)
#hex_table_as_tibble
```

